Testing the precision of Bangla Communication Scale: Item Response Theory Guided Analysis

### 2022-02-04 manuscript.Rmd
Study 2 introduction and objectives

```{r ParallelEFA, include=FALSE}
#This chunk holds code for factor identification method : Horn
# Parallel analysis
Horn <- paran(mat=correlations$rho, iterations=500, centile=0, quietly=FALSE,
           status=TRUE, all=FALSE, cfa=FALSE, graph=TRUE,
           color=TRUE, col=c("black","red","blue"),
           lty=c(1,2,3), lwd=1, legend=TRUE, 
           width=640, height=640, grdevice=png, seed=0, n=300)

@@

>>>>

```{r ParallelEFA, include=FALSE}
#This chunk holds code for factor identification method : Horn
# Parallel analysis
Horn <- paran(mat=correlations$rho, iterations=500, centile=0, quietly=FALSE,
           status=TRUE, all=FALSE, cfa=TRUE, graph=TRUE,
           color=TRUE, col=c("black","red","blue"),
           lty=c(1,2,3), lwd=1, legend=TRUE, 
           width=640, height=640, grdevice=png, seed=0, n=300)

@@

# Study 2 Confirmation of Factor Structure and Psychometric Properties of Bangla Communication Scale

This study had fourth objectives. First, we confirmed the one factor solution of our scale obtained in Study-1. Second, to gather convergent validity evidence of BCS. For this, we calculated the bivariate correlation among the scores of Bangla Communication Scale and Bangla Hopeless Scale. Third, we establised gender-based measurement invariance of Bangla Communication Scale.  Lastly, we assessed item discrimination, item difficulty and precision of BCS using Item Respons Theory Based Analysis
